---
title: "Weight of Fish"
author: "Lelainy Saavedra"
date: "November 3, 2020"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```
```{r}
Fishdata=read.csv("Fish.csv", header=TRUE)
```


# Introduction
In this Analysis we are trying to predict which is the best regression model to  that can predict weight of perch.  

$H_0$: There is No best model that works best to predict the weight of Perch.  
$H_A$: There is a better model that can help us predict the weight of perch.  
<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

## Build the best regression model you can that predicts the weight of perch
## Using only two predictor variables  


# Methods  
We are using numerical~numerical because the variables we are looking are all numerical variables.  
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

#Results


<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
## PERCH DATA

```{r}
Fishies=filter(Fishdata, Species== "Perch")
Fishies = select(Fishies, -Species)
pairs(Fishies)

```
In this model it shows that the best ans straightest line would be lenght 1.
```{r}
summary(Fishies)
```
```{r}
perchmodel=lm(Weight~Length2+Width, data=Fishies)
summary
```
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data=Fishies,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

## BREAM DATA
```{r}
FishiesB=filter(Fishdata, Species == "Bream")
FishiesB = select(FishiesB,-Species)
pairs(FishiesB)
```
```{r}
Perchmodel=lm(Weight~Length2+Width,data=FishiesB)
summary(Perchmodel)
```
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data=FishiesB,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
## SMELT  DATA
```{r}
FishiesS=filter(Fishdata, Species == "Smelt")
FishiesS = select(FishiesS,-Species)
pairs(FishiesS)
```
```{r}
Perchmodel3=lm(Weight~Length2+Width,data=FishiesS)
summary(Perchmodel)
```

```{r}
Perchmodel3=lm(Weight~Length2+Width,data=FishiesS)
summary(Perchmodel)
```
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data=FishiesS,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


# Discussion and Conclusion

Based on the models we used to predict the best prediction model, it seems that the first model is the best model to use when determining the weight of perch.

For the Beam species it appears that the best regression model would include the variable lenght1 along with the variable weigt and width. Using these variables for our summary bream  model 2 and our subset models, it would appear that the best model to usewould be the subset model with an adjusted R square of 0.934.  
For the Smelt species it appears that the best regression model is that of variable lenght3 along with weight and width.
<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


